### 2023-10-24 manuscript.tex
Added TODO notes for revisions
Added citation to ortholog generation

@@

@@

@@

@@

@@

@@

\section{Materials and methods}
\subsection{Alignment and species tree provenance}
Alignments of 8,566 single copy orthologs and the corresponding outputs of the missing data phylo-HMM were obtained from the analyses conducted in chapter~\ref{chapter:1}. Likewise, the LG consensus tree generated by the ``non-invariant, 100\% redundancy'' sampling strategy was used as the input or reference where indicated in subsequent phylogenetic analyses.

@@

>>>>

% TODO: Add sentence(s) about searching regions against Pfam domains and measuring overlap
% We also searched the database of Pfam domains against the full-length D. melanogaster proteins in these alignments and measured their overlap with the called disorder and order regions. The results show a clear enrichment in the disorder regions having no or only small amounts of overlap relative to the order regions.

@@

% TODO: Add paragraph investigating statistical properties of hypothesis testing
% As both the BM and OU models are fully probabilistic, the data's relative support for the more complex OU model is quantified by the difference of its log-likelihood relative to that of the BM model. Because greater a log-likelihood indicates more support for a given model, a greater difference in log-likelihood indicates more support for the OU model over the BM model. However, to directly relate these differences to the probability of a type I error and to assess other statistical properties of the models under the hypothesis testing framework , we conducted a set of simulations.
% We simulated data under each model using the species tree and a range of parameter values. However, because the likelihood of a model is unchanged if the mean and observations are shifted by a constant, we fixed the mean and optimal values of the BM and OU models to zero during our simulations.
% Discuss estimations of model parameters when model is concordant with data generation process
%   - Make plots of mean estimates for both
%   - Re-scale OU heatmaps to calculate error
% This paragraph needs its own figure with panels for estimates of each model and type I/II error plots

@@

% TODO: Re-write above paragraph to move directly into discussion of global properties of conserved features
% What is the distribution of number of ``conserved'' features across regions at a given cutoff?
% What fraction of IDRs has each feature conserved?
% Show some examples of IDRs with certain conserved features and plots of delta log-likelihoods with cutoffs indicated

@@

% TODO: Merge some of introduction from previous paragraph into this in order to introduce idea of investigating existence of global patterns of signatures
% Include some controls used in Zarin to ensure clustering is not based on sequence similarity
% Expand discussion of individual clusters, including specific conserved features and associated biological functions

@@

% TODO: Re-write this paragraph to reflect updates in results and additional analyses of clusters
% Note any qualitative similarities or differences to yeast clusters

@@

% TODO: Add note about annotations not at level of regions
% That proteins are annotated at the level of entire sequences further compounds these issues, as it is unclear that if annotations are specifically associated with the IDRs in the identified clusters.

@@

\section{Materials and methods}
\subsection{Alignment and species tree provenance}
Alignments of 8,566 single copy orthologs and the corresponding outputs of the missing data phylo-HMM were obtained from Singleton \textit{et al.}~\cite{Singleton2023}. Likewise, the LG consensus tree generated by the ``non-invariant, 100\% redundancy'' sampling strategy was used as the input or reference where indicated in subsequent phylogenetic analyses.

@@

% TODO: Add Pfam overlap subsection
